### 2014-01-31 inst/vign/taxize_vignette.Rmd
changed vignettes to not build during pkg install, new makefile

<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{An R Markdown Vignette made with knitr}
-->

@@

```{r installtaxizecran, eval=FALSE}
install.packages("taxize")
library(taxize)
```

@@

```{r resolvenames, eval=TRUE, cache=FALSE}
library(taxize)
temp <- gnr_resolve(names = c("Helianthos annus", "Homo saapiens"))
temp[ , -c(1,4)]
```

@@

```{r tnrs, eval=TRUE, cache=FALSE}
mynames <- c("Helianthus annuus", "Pinus contort", "Poa anua", "Abis magnifica",
  	"Rosa california", "Festuca arundinace", "Sorbus occidentalos","Madia sateva")
tnrs(query = mynames, getpost="GET")[ , -c(5:7)]
```

>>>>

<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{taxize vignette}
-->

@@

```{r installtaxizecran, eval=FALSE}
install.packages("taxize")
```

```{r loadtaxize, messages=FALSE, warning=FALSE}
library(taxize)
```

@@

```{r resolvenames, eval=TRUE, cache=FALSE}
temp <- gnr_resolve(names = c("Helianthos annus", "Homo saapiens"))
temp[ , -c(1,4)]
```

@@

```{r tnrs, eval=TRUE, cache=FALSE}
mynames <- c("Helianthus annuus", "Pinus contort", "Poa anua", "Abis magnifica",
  	"Rosa california", "Festuca arundinace", "Sorbus occidentalos","Madia sateva")
tnrs(query = mynames, source = "iPlant_TNRS")[ , -c(5:7)]
```
